### 2020-06-25 introduction.tex
cl for abs and intro

\vspace{1mm}
\noindent
\textbf{challenges.} Creating a high-resolution shoulder surfing attack model running on commercial smartphones in real time, however, is not trivial. And we achieve \textsf{SRPeek} by overcoming three key challenges.

@@

\cl{The following part can correspond to challenges above.}
In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing for commercial smartphones. To fully explore this privacy threat with the multi-frame super resolution, we first design a deep learning architecture using convolutional neural network (CNN). With the specially designed network as core, we deliver a holistic system for shoulder surfing on a smartphone. Then it processes them with our neural network to generate a high-resolution image and repeats the process for constant monitoring. As the information of interest is mostly in the form of text (e.g., passwords or e-mails), our network is trained and evaluated on the task of reconstructing text, specifically, Chinese characters, English letters, and numbers, but we believe that this network architecture can function in all scenarios. Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition on self-driving cars.

@@

% The details of our architecture will be discussed in section 4.
This paper makes the following contributions:
\begin{itemize}
  \item	We propose \textsf{SRPeek}, a multi-frame SR neural network architecture aiming at reconstructing extremely blurred and defocused images. This model is not only functional in our scenario, as a shoulder-surfing threat model, but also can be used in text-recognition applications prior to recognition algorithms to increase accuracy.
  \item	We design a threat model of shoulder-surfing, with the attacker armed with multi-frame SR algorithms and taking multiple photos (in burst mode) of the victim’s screen with a smartphone camera. To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
  \item	We demonstrate the effect of this shoulder-surfing attack and prove that it poses a threat to screen privacy.
\end{itemize}

>>>>

\cl{The challenge part can be revised to make it more precise. And it can be described with the new figure.}
\vspace{1mm}
\noindent
\textbf{challenges.} Creating a high-resolution shoulder surfing attack model running on commercial smartphones in real time, however, is not trivial. And we achieve \textsf{SRPeek} by overcoming three key challenges.

@@

\cl{The following part can correspond to challenges above. Remember to be precise and illustrative.}
In this paper, we present \textsf{SRPeek}, an end-to-end system of shoulder surfing for commercial smartphones. To fully explore this privacy threat with the multi-frame super resolution, we first design a deep learning architecture using convolutional neural network (CNN). With the specially designed network as core, we deliver a holistic system for shoulder surfing on a smartphone. Then it processes them with our neural network to generate a high-resolution image and repeats the process for constant monitoring. As the information of interest is mostly in the form of text (e.g., passwords or e-mails), our network is trained and evaluated on the task of reconstructing text, specifically, Chinese characters, English letters, and numbers, but we believe that this network architecture can function in all scenarios. Our system can also be used as a preprocessor for text-recognition applications when multiple images are available, such as real-time translation apps on a smartphone or text-recognition on self-driving cars.

@@

\cl{Evaluations can be summarized here (performance and comparison with existing works).}

\vspace{1mm}
\noindent
\textbf{Summary of Evaluation Results.}

\vspace{1mm}
\noindent
\textbf{Contributions.} This paper makes the following contributions:
\begin{itemize}[leftmargin=*]
  \item	We propose \textsf{SRPeek}, a multi-frame SR neural network architecture aiming at reconstructing extremely blurred and defocused images. This model is not only functional in our scenario, as a shoulder-surfing threat model, but also can be used in text-recognition applications prior to recognition algorithms to increase accuracy.
  \item	We design a threat model of shoulder-surfing, with the attacker armed with multi-frame SR algorithms and taking multiple photos (in burst mode) of the victim’s screen with a smartphone camera. To the best of our knowledge, we are the first to consider the presence of smartphone cameras and SR algorithms in shoulder surfing scenarios.
  \item	We demonstrate the effect of this shoulder-surfing attack and prove that it poses a threat to screen privacy.
\end{itemize}
